### 2017-11-14 paper/sections/1_introduction.tex
paper: clear up figure 1
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

In this paper, we design cache management policies for ParSplice, driven by a
detailed analysis of the key-value accesses over the course of a long running
simulation across a variety of initial conditions. The default ParSplice
implementation uses an unlimited sized cache, as shown by the ``No Cache
Management" line Figure~\ref{fig:cache-management}. Using this much memory for
one cache is unacceptable for HPC environments, where memory is precious and a
common goal is to keep memory for such data structures below
3\%\footnote{Empirically, we find this threshold works well for most
applications}.  While users can configure ParSplice to resize the cache when it
reaches a certain threshold, this solution requires tuning and parameter sweeps
to find the optimal cache size that sacrifices negligible performance. The
dashed ``Cache (too small)" curve in Figure~\ref{fig:cache-management} shows
how a poorly configured cache hurts performance.  Our final solution, shown by
the ``Dynamically Sized Cache" line in Figure~\ref{fig:cache-management},
detects keyspace access patterns and re-sizes the cache accordingly.  Without
tuning or parameter sweeps, our solution saves more memory than a hand-tuned
cache without sacrificing performance.  More importantly, it works for a
variety initial conditions without changing the policy itself.

% What is Mantle
To design more flexible cache management policies, like our ``Dynamically
Sized Cache" policy, we use the data management language and policy engine
from the Mantle paper~\cite{sevilla:sc15-mantle}. This framework allows us to
dynamically explore the effects of different software-defined cache management
strategies for the changing key-value workloads generated by ParSplice.  Mantle
was originally touted as a programmable file system metadata load balancer, but
we realize now that the collection of abstractions designed for file systems
was a control plane that improved metadata access. So in this paper we refer to
Mantle as a policy engine that injects policies written in our data management
language directly into a running service and show how this approach is useful
for reasoning about and designing different cache management strategies in
ParSplice.  By service, we mean a system that manages data and responds to
requests, such as a file system or key-value store.  Developers write policies
for ``when" they want data moved and ``how much" of the data to move, then the
framework executes these policies whenever a decision needs to be made.  These
abstractions help developers unfamiliar with the domain quickly reason about,
develop, and deploy new policies that control temporal and spatial locality. We
show that Mantle:

>>>>

In this paper, we design cache management policies for ParSplice, driven by a
detailed analysis of the key-value accesses over the course of a long running
simulation across a variety of initial conditions.

The memory usage for a ParSplice cache that stores molecule coordinates is
shown in Figure~\ref{fig:cache-management}. The solid lines are the existing
cache management policies, exposed as configurations in ParSplice.  The default
ParSplice configuration uses an unlimited sized cache, shown by the ``No Cache
Management" line, but using this much memory for one cache is unacceptable for
HPC environments, where memory is precious and a common goal is to keep memory
for such data structures below 3\%\footnote{Empirically, we find this threshold
works well for most applications}.  While users can configure ParSplice to
resize the cache when it reaches a certain threshold, this solution requires
tuning and parameter sweeps to find the optimal cache size that sacrifices
negligible performance.  Furthermore, this threshold changes with different
initial configurations and clusters, as shown by our keyspace analysis in
Section~\S\ref{sec:parsplice-keyspace-analysis}.  The ``Cache (too small)"
curve in Figure~\ref{fig:cache-management} shows how a poorly configured cache
can save memory but at the expense of performance.  Our dynamically sized
cache, shown by the dashed line in Figure~\ref{fig:cache-management} detects
keyspace access patterns and re-sizes the cache accordingly.  Without tuning or
parameter sweeps, our solution saves more memory than a hand-tuned cache
without sacrificing performance.  More importantly, it works for a variety
initial conditions without changing the policy itself.

% What is Mantle
To design more flexible cache management policies, like our dynamically sized
cache solution in Figure~\ref{fig:cache-management}, we use the data management
language and policy engine from the Mantle paper~\cite{sevilla:sc15-mantle}.
This framework allows us to dynamically explore the effects of different
software-defined cache management strategies for the changing key-value
workloads generated by ParSplice.  Mantle was originally touted as a
programmable file system metadata load balancer, but we realize now that the
collection of abstractions designed for file systems was a control plane that
improved metadata access. So in this paper we refer to Mantle as a policy
engine that injects policies written in our data management language directly
into a running service and show how this approach is useful for reasoning about
and designing different cache management strategies in ParSplice.  By service,
we mean a system that manages data and responds to requests, such as a file
system or key-value store.  Developers write policies for ``when" they want
data moved and ``how much" of the data to move, then the framework executes
these policies whenever a decision needs to be made.  These abstractions help
developers unfamiliar with the domain quickly reason about, develop, and deploy
new policies that control temporal and spatial locality. We show that Mantle:
